---
title: "COVID-19 Impact: Dagahaley Refugee Camp"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE, message = F, warning = F, results = F}
require(knitr)
require(tidyverse)
require(gridExtra)
library(doParallel)
# require(rstan)
library(RColorBrewer)
#library(RgoogleMaps)
library(pander)
library(kableExtra)

options(scipen = 999)
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../"))

```

```{r include=FALSE, message = F, warning = F, results = F}
source("R/DataLoadUtils.r")
source("R/BasicEpiAnalyses.r")
source("R/DataUtils.r")
source("R/model_functions.R")
source("R/StochasticSEIR.R")
source("R/CalcHospDeaths.R")
source("R/get_ageadjust_severe.R")
```



<!-- ONLY NEED TO CHANGE THE FOLLOWING CHUNK -->

```{r, include=FALSE, message = F, warning = F, results = F}

# Project location
project <- "dagahaley"
location_name <- "Dagahaley Refugee Camp"

# Population Size
N <- 200000
N_beds = N/1000


```




<center> The Potential Impact of COVID-19 in the `r print(location_name)` </center>
<center> Shaun Truelove, Natalya Kostandova, Andrew Azman </center>
        
<center> `r print(format(as.Date(Sys.Date()), "%d %B %Y") )` </center>

    

```{r, include=FALSE, message = F, warning = F, results = F}
# Create all the folders
dir.create(file.path("data",project), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("results",project), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("figures",project), recursive = TRUE, showWarnings = FALSE)
```







<!--
## PROPORTION SEVERE

In a setting such as a refugee setting we will assume hospitalization will be limited to those who most require it, specifically severe cases. We assume all hospitalization capacity available will be shifted for responding to COVID-19 severe cases, and no hospitalization for purposes of isolation will be done. Under these assumptions, we can assume the proportion of infections that result in severe disease approximate the proportion that will require hospitalization.

While we are still trying to understand who is most at risk for severe disease and what proporiton of individuals infected will eventually develop severe disease and die, we do know that this is highly dependent on age. To get an appropriate estimate of severity in different populations, we will use estimates of proportion severe by age to adjust by the populations age distribution and get an overall proportion severe for the population of interest.


### Estimate proportions severe by age, using data from Shenzhen, China (Bi et al. 2020)

We will use bayesian methods to estimate the proportion severe by age, using data from Shenzhen, China (Bi et al. 2020). --> 

```{r, include=FALSE, message = F, warning = F, results = F}
# Run Stan Model to estimate probability severe by age
prop_severe_ests <- get_severe_age_shenzhen( )

```
    
<!--    
### Application to Age Distributions

Now we can apply these estimates to age distributions of different locations. --> 

```{r, include=FALSE, message = F, warning = F, results = F}

# USA
p_usa <- get_p_severe(country="United States of America")

# Bangladesh
p_bgd <- get_p_severe(country="Bangladesh")

# China
p_chn <- get_p_severe(country="China")

# Italy
p_ita <- get_p_severe(country="Italy")

# Switzerland
p_che <- get_p_severe(country="Switzerland")


p_data <- bind_rows(data.frame(Location = "USA", p_severe=p_usa$ests),
                    data.frame(Location = "China", p_severe=p_chn$ests),
                    data.frame(Location = "Bangladesh", p_severe=p_bgd$ests),
                    data.frame(Location = "Italy", p_severe=p_ita$ests),
                    data.frame(Location = "Switzerland", p_severe=p_che$ests)) %>%
  mutate(Location=factor(Location, levels=c("Bangladesh","China","USA","Switzerland","Italy"), ordered = TRUE))

 # Make some boxplots
# ggplot(p_data, aes(x=Location, y=p_severe)) +
#   geom_boxplot(fill="maroon", color="darkred") + 
#   ylab("Proportion Severe")
  
write_csv(p_data, 
          file.path("results", project, "p_data.csv"))

```



<!--
### Proportion Severe, Dagahaley expansion site
    
Now we need to apply the population structure of Dagahaley to estimate proportion hospitalized there.-->

```{r, include=FALSE, message = F, warning = F, results = F}

#pr_age10 <- read_csv(file.path("data",project, "age_dagahaley.csv"))

pr_age10 <- read_csv(file.path("data", "age_dagahaley.csv"))


# Estimate the proportion severe in the camp
p_severe_dagahaley <- get_p_severe_pop(pr_age10$p)
save(p_severe_dagahaley, file=file.path("results", project, "p_severe_dagahaley.RData"))



# PLOT IT
p_data <- bind_rows(p_data, data.frame(Location = stringr::str_to_title(project), p_severe=p_severe_dagahaley$ests)) %>%
  mutate(Location=factor(Location, 
                         levels=c(stringr::str_to_title(project), "Bangladesh","China","USA","Switzerland","Italy"), 
                         ordered = TRUE)) %>%
  mutate(col_ = ifelse(Location==stringr::str_to_title(project), 2, 1))

# Make some boxplots
fills <- c("1"="maroon", "2"="gold")
cols <- c("1"="darkred", "2"="goldenrod1")
plot_severity <- ggplot(p_data, aes(x=Location, y=p_severe, fill=factor(col_), colour=factor(col_))) +
                          geom_boxplot() + 
                          scale_color_manual(values=c("darkred", "goldenrod4")) +
                          scale_fill_manual(values=c("maroon", "goldenrod1")) +
                          ylab("Proportion Severe") +
                          theme(legend.position = "none")
                        

```

<!--
Based on this crude analysis, if we assume 75% of infections in those 70+ lead to hospitalization, and the odds of hospitalization given infection by age mirrors the odds of mortality by age, we find that the hospitalization rate in `r print(stringr::str_to_title(project))` is likely to be between 4.9-9.2%, compared with 14.0-21.8% in China. From these estimates, it is reasonable to assume infections in Dagahaley are 35-43% as likely to result in a hositalization, as compared to China.



# PARAMETERS

### R0 Estimates Check --> 
```{r, include=FALSE, message = F, warning = F, results = F}
r0 <- c(2.68,2.24,0.3,1.44,2.1,3.2,7.05,2.4,2.4,4.7,6.6,
        3.24,2.45,1.48,3.1,1.6,3.11,2.5,2.6,2.2)

R0quants <- quantile(r0, c(0.025, .975))

```



<!-- ## Model Parameters --> 

```{r, include=FALSE, message = F, warning = F, results = F}

# Simulation specifics   ----------------------------------------------
n.sims <- 500 # simulations per R
n.Rs <- 20
run_time <- 550
start_date_="2020-03-15"
end_date <- "2022-01-01"
step.size <- 1/8
seeds <- 1
cores <- 4


# Transmission Characteristics ---------------------------------
# we are going to assume recovery has mean of 7 days from infection
# then we will use a beta consistent with our estimates from above
# https://github.com/midas-network/COVID-19/tree/master/parameter_estimates/2019_novel_coronavirus

# incubation period 5.2 days based on an estimate from Lauer et al. 2020
sigma <- 1/(5.2) # subtract 1 for latent period adjustment
# time from symptom onset to recovery  
n_Icomp <- 3 # number of I compartments (using 3 to capture Erlang distribution)
gamma <-  1/6 * n_Icomp 



# R0 Values  ----------------------------------------------

# Controlled transmission 
R0_low <- runif(n.Rs, 1.5,2)
# Moderate transmission
R0_mid <- runif(n.Rs, 2, 3)
# Inflated transmission (inflated by the diphtheria inflation factor)
R0_high <- runif(n.Rs, 2*1.65, 3*1.65)


# sample point estimates of our betas from above
betas_low <- R0_low   * gamma / n_Icomp
betas_mid <- R0_mid   * gamma / n_Icomp
betas_high <- R0_high * gamma / n_Icomp






# Hospitalization   ----------------------------------------------


# time from hospitalization to discharge mean= 11.5, sd=3.625
# time from hospitalization to death mean= 11.2, sd= 1.88
# Time to hospitalization among symptom-based, mean 4.65 days (95% CI 0.93-12.42) (Bi et al. 2020)
# Time from hospitalization to discharge,  11.5 days (95% CI 8.0-17.3) (Sanche et al. 2020)
# Time from hospitalization to death, 11.2 days (95% CI 8.7-14.9) (Sanche et al. 2020)

#p_hosp  <- c(p_severe_dagahaley, p_hosp_dagahaley_high)
p_death <- .1
p_ICU   <- 0.264
p_vent  <- 0.15

time_hosp_pars = c(1.23, 0.79)
time_death_pars = c(log(11.25), log(1.15))
time_disch_pars = c(log(11.5), log(1.22)) 

```


<!--
# MODEL
    
### Run the model 
We can do this locally or on a cluster if needed. --> 

```{r sim_model, include=FALSE, message = F, warning = F, results = F}
betas <- betas_low
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="low",
                                   sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

betas <- betas_mid
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="mid", sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

betas <- betas_high
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="high", sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

```
    

   
<!-- ### Low Beta --> 
```{r, include=FALSE, message = F, warning = F, results = F}

R0_val <- "low"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val, "-",
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)


# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))


sim_res_full <- sim_hospdeath %>% dplyr::select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "Low") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_low <- sim_res_full
rm(sim_res)

# Save it
dir.create("results", recursive = TRUE, showWarnings = FALSE)
write_csv(sim_res_full, 
          file.path("results", project, paste0("sim_res_low_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```

    
    
    
<!-- ### Mid Beta  --> 
      
```{r, include=FALSE, message = F, warning = F, results = F}

betas <- betas_mid

R0_val <- "mid"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val, "-",
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)



# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))



sim_res_full <- sim_hospdeath %>% select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "Mid") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_mid <- sim_res_full

# Save it
write_csv(sim_res_mid, 
          file.path("results", project, paste0("sim_res_mid", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```

<!--




### High Beta --> 
```{r, include=FALSE, message = F, warning = F, results = F}

betas <- betas_high

R0_val <- "high"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val,"-", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)


# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))



sim_res_full <- sim_hospdeath %>% select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "High") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_high <- sim_res_full

# Save it
dir.create("results", recursive = TRUE, showWarnings = FALSE)
write_csv(sim_res_high,
          file.path("results", project, paste0("sim_res_high_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```


<!--

# RESULTS

### ~ Combine results --> 

```{r, include=FALSE, message = F, warning = F, results = F}

sim_res <- full_join(full_join(sim_res_low %>% mutate(scenario="Low Transmission"),
                               sim_res_mid %>% mutate(scenario="Moderate Transmission")),
                               sim_res_high %>% mutate(scenario="High Transmission"))
sim_res$R <- sim_res$beta * n_Icomp / gamma
sim_res <- sim_res %>% mutate(scenario = factor(scenario, levels=c("Low Transmission", "Moderate Transmission", "High Transmission"), ordered = TRUE))

sim_res <- sim_res %>% filter(!is.na(sim))

write_csv(sim_res, 
          file.path("results", project, paste0("sim_res_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```


```{r, include=FALSE, message = F, warning = F, results = F}
sim_res <- read_csv(file.path("results", project, paste0("sim_res_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))
sim_res <- sim_res %>% 
  mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))
```



<!--

## TABLE 1  -->
        
```{r, include=FALSE, message = F, warning = F, results = F}

# Final Size - IN first 550 days
summ_ <- sim_res %>% as.data.frame() %>% group_by(sim_beta, scenario) %>% 
  summarise(final_size = max(cum_cases, na.rm=TRUE),
            max_daily_incid = max(incidI, na.rm=TRUE),
            max_daily_hosp  = max(incidH, na.rm=TRUE),
            max_daily_icu  = max(incidICU, na.rm=TRUE),
            max_daily_vent  = max(incidVent, na.rm=TRUE),
            max_daily_death  = max(incidD, na.rm=TRUE),
            max_curr_hosp   = max(hosp_curr, na.rm=TRUE),
            max_curr_icu   = max(icu_curr, na.rm=TRUE),
            #max_curr_vent   = max(vent_curr, na.rm=TRUE),
            final_death  = max(cum_death, na.rm=TRUE),
            final_hosp  = max(cum_hosp, na.rm=TRUE),
            final_vent  = max(cum_vent, na.rm=TRUE),
            final_icu  = max(cum_icu, na.rm=TRUE))

final_size_ <- summ_ %>% group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)),
            finalsize10 = mean(final_size>=10, na.rm=TRUE),
            finalsize100 = mean(final_size>=100, na.rm=TRUE),
            finalsize1000 = mean(final_size>=1000, na.rm=TRUE))

final_size_min100 <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)))

final_size_min1000 <- summ_ %>% filter(final_size>=1000) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)))

incid <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_daily_incid, na.rm=TRUE),
            median = median(max_daily_incid, na.rm=TRUE),
            ll = quantile(max_daily_incid, prob=c(.0275)),
            ul = quantile(max_daily_incid, prob=c(.975)))

hosps <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_hosp, na.rm=TRUE),
            median = median(final_hosp, na.rm=TRUE),
            ll = quantile(final_hosp, prob=c(.0275)),
            ul = quantile(final_hosp, prob=c(.975)))

curr_hosp <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_curr_hosp, na.rm=TRUE),
            median = median(max_curr_hosp, na.rm=TRUE),
            ll = quantile(max_curr_hosp, prob=c(.0275)),
            ul = quantile(max_curr_hosp, prob=c(.975)))

hosp_incid <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_daily_hosp, na.rm=TRUE),
            median = median(max_daily_hosp, na.rm=TRUE),
            ll = quantile(max_daily_hosp, prob=c(.0275)),
            ul = quantile(max_daily_hosp, prob=c(.975)))

deaths <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_death, na.rm=TRUE),
            median = median(final_death, na.rm=TRUE),
            ll = quantile(final_death, prob=c(.0275)),
            ul = quantile(final_death, prob=c(.975)))

# Summarize day cum cases exceeds N_beds
hospexceeds <- sim_res %>% group_by(scenario, sim_beta) %>% 
  filter(cum_cases>N_beds) %>%
  summarise( dayexceeds = min(day, na.rm=TRUE)) %>% group_by(scenario) %>%
  summarise(mean=mean(dayexceeds, na.rm=TRUE),
            ll = quantile(dayexceeds, .025, na.rm=TRUE), 
            ul = quantile(dayexceeds, .975, na.rm=TRUE))



table1 <- final_size_min100 %>% mutate(pr_outbreak=final_size_$finalsize100) %>%
  mutate(tot_inf = paste0(round(mean), " (",round(ll),"-",round(ul),")"),
          tot_hosp = paste0(round(hosps$mean), " (",round(hosps$ll),"-",round(hosps$ul),")"),
          tot_deaths = paste0(round(deaths$mean), " (",round(deaths$ll),"-",round(deaths$ul),")"),
          max_incid = paste0(round(incid$mean), " (",round(incid$ll),"-",round(incid$ul),")"),
          max_hosp_incid = paste0(round(hosp_incid$mean), " (",round(hosp_incid$ll),"-",round(hosp_incid$ul),")"),
          max_hosp_curr = paste0(round(curr_hosp$mean), " (",round(curr_hosp$ll),"-",round(curr_hosp$ul),")"),
          day_hosp_exceed = paste0(round(hospexceeds$mean), " (",round(hospexceeds$ll),"-",round(hospexceeds$ul),")"),) %>%
  select(scenario, pr_outbreak, tot_inf, tot_hosp, tot_deaths, max_incid, max_hosp_incid, max_hosp_curr, day_hosp_exceed)

#table1
write_csv(table1, file.path("results", project, "Table1.csv"))


```






```{r, include=FALSE, message = F, warning = F, results = F}

# case_data <- read_csv("data/case_data.csv")
# hubei_cases <- case_data %>% filter(Province_State=="Hubei") %>% arrange(t)
# hubei_cases$est_infections <- hubei_cases$est_incid / p_hosp_china_low

sim_res_summ <- sim_res %>% group_by(scenario, day) %>% 
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

```




```{r, include=FALSE, message = F, warning = F, results = F}

sim_res_outbreaks <- sim_res %>% group_by(scenario, sim_beta) %>% 
  mutate(sim_max = max(cum_cases, na.rm = TRUE)) %>%
  filter(cum_cases > 100 ) 
  
sim_res_summ_outbreak <- sim_res_outbreaks %>% group_by(scenario, day) %>% 
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

```



<!--
## TABLE 2 -->


```{r, include=FALSE, results=FALSE}

max_day_datahigh <- sim_res_outbreaks %>% filter(scenario=="High Transmission") %>% 
  group_by(sim_beta) %>% mutate(maxday = max(day), na.rm=TRUE) %>% ungroup() %>% filter(day==maxday)

max_day_datamid <- sim_res_outbreaks %>% filter(scenario=="Moderate Transmission") %>% 
  filter(day<=365) %>%
  group_by(sim_beta) %>% mutate(maxday = max(day), na.rm=TRUE) %>% ungroup() %>% filter(day==maxday)


sim_res_summ_outbreak_days <- sim_res_outbreaks %>% filter(day %in% c(30, 91, 182, 365)) %>%
  group_by(day, scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

sim_res_summ_outbreak_daysHigh <- max_day_datahigh %>%
  group_by(scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))


sim_res_summ_outbreak_daysModerate <- max_day_datamid %>%
  group_by(scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))



sim_res_summ_outbreak_days <- bind_rows(sim_res_summ_outbreak_days,
                                        sim_res_summ_outbreak_daysModerate %>% mutate(day=365),
                                        sim_res_summ_outbreak_daysHigh %>% mutate(day=365))

table2 <- sim_res_summ_outbreak_days %>% group_by(scenario, day) %>%
  mutate(cum_inf = paste0(round(cum_mean), " (",round(cum_ll),"-",round(cum_ul),")"),
         cum_hosp = paste0(round(hosp_cum_mean), " (",round(hosp_cum_ll),"-",round(hosp_cum_ul),")"),
         cum_icu = paste0(round(icu_cum_mean), " (",round(icu_cum_ll),"-",round(icu_cum_ul),")"),
         cum_vent = paste0(round(vent_cum_mean), " (",round(vent_cum_ll),"-",round(vent_cum_ul),")"),
         cum_death = paste0(round(death_cum_mean), " (",round(death_cum_ll),"-",round(death_cum_ul),")")) %>%
  select(scenario, day, cum_inf, cum_hosp, cum_icu, cum_vent, cum_death)
  #mutate(scen_day = paste0(scenario," - ",day)) %>% select(-scenario, -day) 

# table2
write_csv(table2, file.path("results", project, "Table2.csv"))


#View(data.frame(sim_res_summ_outbreak_days[,c(1:2)], round(sim_res_summ_outbreak_days[,-c(1:3)] / 600000,2)))


```


<!-- ### Time intervals -->

```{r, include=FALSE, message = F, warning = F, results = F}

View(sim_res_summ_outbreak %>% filter(day==30) %>%
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))


View(sim_res_summ_outbreak %>% filter(day==60) %>% 
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))

View(sim_res_summ_outbreak %>% filter(day==90) %>% 
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))


```






<!--# FIGURES


### Age Distribution and Severity profiles -->
```{r, echo=FALSE}
#
#plot_age <- ggplot(pr_age10, aes(x=age_group, y=p)) +
#                    geom_bar(stat="identity", color="navyblue", fill="navyblue", width = .95) +
#                    coord_flip() +
#                    xlab("Proportion") +
#                    ylab("Age (y)")
#
#gridExtra::grid.arrange(plot_age, plot_severity, ncol=2)
#ggsave(file.path("figures", project, "age_severity.png"), 
#       gridExtra::grid.arrange(plot_age, plot_severity, ncol=2), 
#       width=10, height=5, dpi=900, units = "in")

```

    
    
<!--
### 3-Curve Panel   -->

```{r, include=FALSE, results=FALSE}

# Incid mean
sim_res_summ <- sim_res_summ %>% as.data.frame() %>%
                    mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))


pincid <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=incid_ll, ymax=incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    # geom_line(data=hubei_cases, aes(x=0:(nrow(hubei_cases)-1), y=est_infections), color="grey50", alpha=.5, size=1.5) +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.8),
          legend.title = element_blank()) +
          scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    ylab("Incident infections") + xlab("Day") +
  ggtitle("Estimated daily incident infections")

pincidhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    theme_classic() + 
    scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    #geom_hline(yintercept = 250, col="red", linetype="dashed") +
    theme(legend.position = "none") +
    ylab("Daily hospitalizations") + xlab("Day") +
  ggtitle("Estimated daily hospitalizations")

# pincidhosp_vHubei <- ggplot(data=sim_res_summ, aes(x=day)) +
#     geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
#     geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
#     geom_line(data=hubei_cases, aes(x=(0:(nrow(hubei_cases)-1)+30), y=est_incid), 
#               color="grey50", alpha=.5, size=1.5) +
#     #scale_y_continuous(trans="log") +
#     theme_classic() + 
#         scale_color_brewer(palette = "Set1", direction = -1) +
#     scale_fill_brewer(palette = "Set1", direction = -1) +
#       geom_hline(yintercept = 250, col="red", linetype="dashed") +
# 
#     theme(legend.position = "none") +
#     ylab("Daily hospitalizations") + xlab("Day") +
#   ggtitle("Estimated hospitalizations, Dagahaley refuge camp versus those observed in Hubei, China")

pinciddeath <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=death_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=death_incid_ll, ymax=death_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    theme_classic() + 
        scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    theme(legend.position = "none") +
    ylab("Daily deaths") + xlab("Day") +
  ggtitle("Estimated daily deaths")



# Cum Infections
pcuminf <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=cum_ll, ymax=cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
        scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative infections") + xlab("Day") +
  ggtitle("Cumulative infections")


# Cum Hospitalizations
pcumhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_cum_ll, ymax=hosp_cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
      scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative hospitalizations") + xlab("Day") +
  ggtitle("Cumulative hospitalizations")


# Cum Deaths
pcumdeath <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=death_cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=death_cum_ll, ymax=death_cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
      scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative deaths") + xlab("Day") +
  ggtitle("Cumulative deaths")


p_panel <- gridExtra::grid.arrange(pincid,pincidhosp,pinciddeath, nrow=3)
ggsave(file.path("figures", project, "sim_res_panel.png"), p_panel, width=8, height=10, dpi=900, units = "in")


```

<!--
### Hospitalization Capacity Needs -->

```{r, include=FALSE, results=FALSE}

# Current Hospitalizations
pcurrhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_curr_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_curr_ll, ymax=hosp_curr_ul, group=scenario, fill=scenario), alpha=.3) + 
    geom_hline(yintercept = 250, col="red", linetype="dashed") +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
  theme(legend.position = c(0.8, 0.8),
          legend.title = element_blank()) +
    ylab("Current hospitalized") + xlab("Day") +
        scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
  ggtitle("Daily hospitalization capacity required")



ggsave(file.path("figures", project, "curr_hosp.png"), width=8, height=4, dpi=600, units = "in")

```

<!--
### Day 20th Case -->

```{r, include=FALSE, results=FALSE, echo=FALSE}

sim_res_nooutbreak <- sim_res %>% group_by(scenario, sim_beta) %>% 
  mutate(max_cum = max(cum_cases)) %>% ungroup() %>%
  filter(max_cum <=1000) %>% 
  filter(cum_cases==max_cum) %>%
  group_by(scenario, sim_beta) %>% filter(day==max(day))

summary(sim_res_nooutbreak$max_cum)
#hist(sim_res_nooutbreak$max_cum)



# First Date >20 cases
sim_res <- sim_res %>% as.data.frame() %>%
                    mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))

day20case <- sim_res %>% filter(cum_cases>=20) %>% group_by(sim_beta, scenario) %>% summarize(minday = min(day)) 
day20case_sum <- day20case %>% group_by(scenario) %>% 
  summarize(mean = mean(minday), 
            median = median(minday),
            ll = quantile(minday, prob=c(.0275)),
            ul = quantile(minday, prob=c(.975)))

p_day20 <- ggplot(day20case, aes(x=minday, group=scenario, fill=scenario)) + 
  geom_density(alpha=0.5) +
  theme_classic() + 
  coord_cartesian(xlim=c(0,150)) +
  xlab("Day") + 
  theme(legend.position = c(0.8, 0.8)) +
  ggtitle("Day on which cumulative cases reaches 20")
#p_day20

ggsave(file.path("figures", project, "day_20th_case.png"), p_day20, width=8, height=4, dpi=900, units = "in")

```


    
```{r, include=FALSE}
### Hospitalization Rate Ratio   

p_severe_dagahaley$mean / p_chn$mean

```
   

<!--   
### Cumulative cases before hospitalizations -->

```{r, echo=FALSE}

hosp_1 <- sim_res %>% filter(cum_hosp>0) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))
# summary((hosp_1 %>% filter(scenario=="High Transmission"))$day)
# summary((hosp_1 %>% filter(scenario=="Moderate Transmission"))$day)
# summary((hosp_1 %>% filter(scenario=="Low Transmission"))$day)




hosp_10 <- sim_res %>% filter(cum_hosp>9) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))
# summary((hosp_10 %>% filter(scenario=="High Transmission"))$day)
# summary((hosp_10 %>% filter(scenario=="Moderate Transmission"))$day)
# summary((hosp_10 %>% filter(scenario=="Low Transmission"))$day)



hosp_20 <- sim_res %>% filter(cum_hosp>19) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))


# print(hosp_1)
# print(hosp_10)
# print(hosp_20)

```


<!--
### Max hospitalization capacities -->

```{r, echo=FALSE}

hosp_capmax <- sim_res %>% filter(cum_cases>100) %>% group_by(scenario, sim_beta) %>% 
  mutate(max_hosp_cap = max(hosp_curr)) %>% ungroup() %>%
  filter(hosp_curr==max_hosp_cap) %>% group_by(scenario) %>% 
  summarise(maxhospday = mean(day), 
            ll = quantile(day, c(.025)), 
            ul = quantile(day, c(.975)))

#print(hosp_capmax)

```










<!-- THIS IS THE SUMMARY  -->
    
## Summary
    
### Background

As of March 19, 2020, globally, there are over 244,500 confirmed cases of COVID-19, the infection caused by the newly emerged severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2). Displaced populations, especially those who reside in settlements with high density, poor access to water and sanitation, and limited health services, are especially vulnerable to a serious outbreak. Kenya, where 7 cases of COVID-19 have been confirmed so far, hosts over 200,000 refugees from Somalia and other countries in the Dadaab refugee complex, with over 73,000 of them residing in `r print(location_name)`. Until recently, Dadaab was the largest refugee complex in the world, with three of the camps, including Dagahaley, established almost 30 years ago. With parts of the complex closed in 2019, humanitarian support drastically reduced over the recent years, and the humanitarian and economic effects of the United States travel ban, the capacity to meet the existing needs of this population are limited.  An outbreak of COVID-19 within this population threatens to severely disrupt an already fragile situation.

### Purpose

To explore the potential impact of SARS-CoV-2 virus on refugees in Dagahaley camp to help decision makers develop plan appropriately.

### Methods

We used a scenario-based approach to model transmission in this population after an introduction of the virus. Assuming a stable population, and a single introduction of the virus into the camp, using three different sets of assumptions about the transmission potential of SARS-CoV-2 at this site, we estimated the number of infections, hospitalizations, deaths, and health care needs that might be expected.

### Results

```{r include=FALSE}
sim_res_summ_low = sim_res_summ %>% filter(scenario=="Low Transmission")
sim_res_summ_mid = sim_res_summ %>% filter(scenario=="Moderate Transmission")
sim_res_summ_high = sim_res_summ %>% filter(scenario=="High Transmission")
```


We found that even in a low transmission scenario, a large-scale outbreak was highly likely after a single introduction of the virus into the camp, with `r (round(100*final_size_$finalsize100[1], 0))`% of the simulations leading to an outbreak of at least 100 infections and increasing to `r round(100*final_size_$finalsize100[2],0)`% and `r round(100*final_size_$finalsize100[3],0)`% in moderate and high transmission scenarios, respectively. On average, in the first 30 days of an outbreak following a single introduction, we expect `r round(sim_res_summ_outbreak_days$cum_mean[1],0)` (95% CI, `r round(sim_res_summ_outbreak_days$cum_ll[1],0)` - `r (round(sim_res_summ_outbreak_days$cum_ul[1],0))`), `r (round(sim_res_summ_outbreak_days$cum_mean[2],0))` (95% CI, `r (round(sim_res_summ_outbreak_days$cum_ll[2],0))` - `r (round(sim_res_summ_outbreak_days$cum_ul[2],0))`), and `r (round(sim_res_summ_outbreak_days$cum_mean[3],0))` (95% CI, `r (round(sim_res_summ_outbreak_days$cum_ll[3],0))` - `r (round(sim_res_summ_outbreak_days$cum_ul[3],0))`)  infections in the low, moderate, and high transmission scenarios, respectively. These reach `r (round(final_size_min100$mean[1],0))` (95% CI, `r (round(final_size_min100$ll[1], 0))`  `r (round(final_size_min100$ul[1], 0))`), `r (round(final_size_min100$mean[2],0))` (95% CI, `r (round(final_size_min100$ll[2], 0))`  `r (round(final_size_min100$ul[2], 0))`), and `r (round(final_size_min100$mean[3],0))` (95% CI, `r (round(final_size_min100$ll[3], 0))`  `r (round(final_size_min100$ul[3], 0))`), infections in 12 months, respectively. 

Given the relatively young age distribution in `r print(location_name)`, we estimate that the proportion of infections that lead to severe disease and hospitalization will be approximately half of what has been estimated in China (3.2 % vs 6.6%). However, even in the low transmission scenario, we project that there could be `r (round(deaths$mean[1],0))` (95% CI, `r (round(deaths$ll[1],0))` - `r (round(deaths$ul[1],0))`) deaths at 12 months, rising to `r (round(deaths$mean[3],0))` (95% CI, `r (round(deaths$ll[3],0))` - `r (round(deaths$ul[3],0))`) with the high scenario. In almost all simulations in all scenarios, the hospitalization needs, in terms of beds alone, significantly exceeded capacities. In the absence of serious efforts to reduce transmission potential of the virus (e.g,. drastic reductions in social contacts) and increases in healthcare capacity, SARS-CoV-2 may have a massive toll on residents of `r print(location_name)`.
  
<!-- THIS IS THE MAIN TEXT -->

## Methods 

### Severity estimates
The proportion of infections that result in severe disease was estimated using data from a closed population of contacts of confirmed COVID-19 cases in Shenzhen, China, for which complete data on contact, age, test results, symptoms, and severity were available (Bi et al. 2020). Using a Bayesian binomial model, we estimated the proportion of infections that were severe by 10-year age groups and then applied those estimates to the 10-year age proportions of the camp population to get an overall proportion of infections that will develop into severe disease in the specific population, as a function of age. These estimates do not account for differences in comorbidities, differing attack rates by age due to population mixing characteristics, or various other factors that may be important in this setting.

### Transmission scenarios 
One of the primary drivers of our epidemic simulations is the transmission potential characterized by the basic reproductive number ($R_0$), or the average number of people each infected individual is expected to transmit to assuming no immunity. We considered three potential scenarios with different values of $R_0$: 1) a low transmission scenario based on transmission levels in many of the Chinese provinces with elevated isolation and control practices and an $R_0$ similar to influenza ($R_0=1.5-2.0$); 2) a moderate transmission scenario that mirrors estimates in early stages of the outbreak in Wuhan, China ($R_0=2.0-3.0$); and, 3) a high transmission scenario where we assume that $R_0$ is increased by a factor of 1.65 ($R_0=3.3-5.0$) compared to estimates from open community settings, as was observed during the 2017 diphtheria outbreak. The $R_0$ in each of these scenarios falls within the 95% confidence interval of the current range of estimates for COVID-19$^{28}$. We assumed an Erlang distributed serial interval (time between the onset of symptoms in infector-infectee pairs) with a mean of 6 days (standard deviation = 4.2), and used a stochastic SEIR model to simulate transmission in this population. 

### Hospitalization and mortality
We assume that in this setting hospitalization would be limited to those with severe disease (defined as tachypnea (30 breaths/ min) or oxygen saturation 93% at rest, or PaO2/FIO2 <300, and/or lung infiltrates >50% of the lung field within 24-48 hours), and not used as a means of isolation. Thus, we assumed the hospitalization rate was equivalent to the severe disease rate. Using estimates based on data from Shenzhen, China, we estimated an age-adjusted rate of severe disease, accounting for the age distribution of Dagahaley, and applied this severe disease rate to incident infections from the model simulations. We estimated deaths assuming a 10% case fatality risk rate among hospitalizations/severe disease. We assumed hospitalization occurs a median of 3.42 days after symptom onset (lognormally distributed, sd=0.79), hospitalized cases are discharged after a mean of 11.5 days (95% CI, 8.0-17.3), and deaths occur after a mean of 11.2 days (95% CI, 8.7-14.9). Additionally, early reports from the outbreak in China indicate that mechanical ventilation was required by approximately 25% of patients with severe disease, while the remaining 75% required only oxygen supplementation. 



## Results

### Infections

We found that a large-scale outbreak is highly likely in this population, even under the low transmission scenario, with `r (round(100*final_size_$finalsize100[1], 0))`% of the simulations producing an outbreak of at least 100 infections with a single introduction (Table 1) and increasing to `r (round(100*final_size_$finalsize100[2],0))`% and `r (round(100*final_size_$finalsize100[3],0))`% in the moderate and high transmission scenarios, respectively. On average, in the first 30 days of an outbreak following a single introduction, we expect `r (round(sim_res_summ_outbreak_days$cum_mean[1],0))` (95% CI, `r (round(sim_res_summ_outbreak_days$cum_ll[1],0))` - `r (round(sim_res_summ_outbreak_days$cum_ul[1],0))`), `r (round(sim_res_summ_outbreak_days$cum_mean[2],0))` (95% CI, `r (round(sim_res_summ_outbreak_days$cum_ll[2],0))` - `r (round(sim_res_summ_outbreak_days$cum_ul[2],0))`), and `r (round(sim_res_summ_outbreak_days$cum_mean[3],0))` (95% CI, `r (round(sim_res_summ_outbreak_days$cum_ll[3],0))` - `r (round(sim_res_summ_outbreak_days$cum_ul[3],0))`)  infections in the low, moderate, and high transmission scenarios, respectively. One year after the start of an outbreak, and in the absence of any effective interventions (e.g., vaccination, quarantine) or behavior change, we expect `r (round(final_size_min100$mean[1] / N * 100,0))`% (95% CI, `r (round(final_size_min100$ll[1] / N * 100, 0))` - `r (round(final_size_min100$ul[1] / N * 100, 0))`%) of the population to have been infected under the low scenario, `r (round(final_size_min100$mean[2] / N * 100,0))`% (95% CI, `r (round(final_size_min100$ll[2] / N * 100, 0))` - `r (round(final_size_min100$ul[2] / N * 100, 0))`%) in the moderate scenario, and `r (round(final_size_min100$mean[3] / N * 100,0))`% (95% CI, `r (round(final_size_min100$ll[3] / N * 100, 0))` - `r (round(final_size_min100$ul[3] / N * 100, 0))`%)  in the high transmission scenario (Table 1). 

We found that in all scenarios, epidemic growth is likely to remain relatively slow at the beginning of an outbreak in this population, with limited numbers of infections and few, if any, hospitalizations and deaths during the first three months (Table 2). However, this quickly changes once sufficient infections are in the population, with rapid increases and wide reached spread of the outbreak after six months (Table 2, Figure 2). 

By the time the first hospitalization occurs, we expect `r (round(hosp_1$meanincid[1],0))` (95% CI, `r (round(hosp_1$ll[1],0))` - `r (round(hosp_1$ul[1],0))`) individuals to be infected in the population under the low scenario, assuming homogeneous probability of infection by age. This increases to `r (round(hosp_1$meanincid[2],0))` (95% CI, `r (round(hosp_1$ll[2],0))` - `r (round(hosp_1$ul[2],0))`) and `r (round(hosp_1$meanincid[3],0))` (95% CI, `r (round(hosp_1$ll[3],0))` - `r (round(hosp_1$ul[3],0))`) in the moderate and high scenarios, respectively. When the first hospitalization occurs, we expect the virus to have been circulating in this population for an average of `r (round(hosp_1$day[1],0))`, `r (round(hosp_1$day[2],0))`, and `r (round(hosp_1$day[3],0))` days under the low, moderate, and high transmission scenarios, respectively. 



### Hospitalization and mortality

Adjusted for the age distribution in the `r print(location_name)`, we estimated that 3.2% (95% CI, 0.9-8.7%) of infections in this population would result in severe disease and hospitalization. The maximum daily hospitalization capacity needed in the low, moderate, and high scenarios was `r (round(curr_hosp$mean[1],0))` (95% CI, `r (round(curr_hosp$ll[1],0))`- `r (round(curr_hosp$ul[1],0))`), `r (round(curr_hosp$mean[2],0))` (95% CI, `r (round(curr_hosp$ll[2],0))`- `r (round(curr_hosp$ul[2],0))`), and `r (round(curr_hosp$mean[3],0))` (95% CI, `r (round(curr_hosp$ll[3],0))`- `r (round(curr_hosp$ul[3],0))`) beds, respectively (Table 1). Under the low transmission scenario, hospitalization needs exceeded the hospitalization capacity of `r (N_beds)` beds after `r (round(hospexceeds$mean[1],0))` days (95% CI, `r (round(hospexceeds$ll[1],0))`-`r (round(hospexceeds$ul[1],0))`) while in the high transmission scenario, this occurred after only `r (round(hospexceeds$mean[2],0))` days (95% CI, `r (round(hospexceeds$ll[2],0))`-`r (round(hospexceeds$ul[2],0))`); (Table 1, Figure 3). 

Assuming that `r (p_death*100)`% of severe cases result in death, which puts the infection fatality rate at 0.32% (95% CI, 0.09 - 0.87%), we estimated a total of `r (round(deaths$mean[1],0))` (95% CI, `r (round(deaths$ll[1],0))` - `r (round(deaths$ul[1],0))`), `r (round(deaths$mean[2],0))` (95% CI, `r (round(deaths$ll[2],0))` - `r (round(deaths$ul[2],0))`), and `r (round(deaths$mean[3],0))` (95% CI, `r (round(deaths$ll[3],0))` - `r (round(deaths$ul[3],0))`) deaths in the low, moderate, and high transmission scenarios, respectively (Table 1). In the high transmission scenario, the maximum number of daily deaths is reached on day `r (sim_res_summ_high$day[which.max(sim_res_summ_low$death_incid_high)])`, compared to day `r (sim_res_summ_low$day[which.max(sim_res_summ_low$death_incid_mean)])` and day `r (sim_res_summ_mid$day[which.max(sim_res_summ_mid$death_incid_mean)])` on average in the low and moderate scenarios, respectively (Figure 2).


