---
title: "COVID-19 Impact: Dagahaley Refugee Camp"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE, message = F, warning = F, results = F}
require(knitr)
require(tidyverse)
require(gridExtra)
library(doParallel)
# require(rstan)
library(RColorBrewer)
#library(RgoogleMaps)

options(scipen = 999)
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(echo=TRUE)
#knitr::opts_knit$set(root.dir = normalizePath("../"))

```

```{r include=FALSE, message = F, warning = F, results = F}
source("R/DataLoadUtils.r")
source("R/BasicEpiAnalyses.r")
source("R/DataUtils.r")
source("R/model_functions.R")
source("R/StochasticSEIR.R")
source("R/CalcHospDeaths.R")
source("R/get_ageadjust_severe.R")
```

```{r}

# Project location
project <- "dagahaley"
location_name <- "Dagahaley Refugee Camp"

# Population Size
N <- 73000




```


# <center> The Potential Impact of COVID-19 in the `r print(location_name)` </center>
<center> Shaun Truelove, Natalya Kostandova, Andrew Azman </center>
        
<center> `r print(format(as.Date(Sys.Date()), "%d %B %Y") )` </center>
    

```{r, echo=FALSE}
# Create all the folders
dir.create(file.path("data",project), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("results",project), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("figures",project), recursive = TRUE, showWarnings = FALSE)
```


## PROPORTION SEVERE

In a setting such as a refugee setting we will assume hospitalization will be limited to those who most require it, specifically severe cases. We assume all hospitalization capacity available will be shifted for responding to COVID-19 severe cases, and no hospitalization for purposes of isolation will be done. Under these assumptions, we can assume the proportion of infections that result in severe disease approximate the proportion that will require hospitalization.

While we are still trying to understand who is most at risk for severe disease and what proporiton of individuals infected will eventually develop severe disease and die, we do know that this is highly dependent on age. To get an appropriate estimate of severity in different populations, we will use estimates of proportion severe by age to adjust by the populations age distribution and get an overall proportion severe for the population of interest.


### Estimate proportions severe by age, using data from Shenzhen, China (Bi et al. 2020)

We will use bayesian methods to estimate the proportion severe by age, using data from Shenzhen, China (Bi et al. 2020).

```{r, eval=FALSE}
# Run Stan Model to estimate probability severe by age
prop_severe_ests <- get_severe_age_shenzhen( )

```
    
    
### Application to Age Distributions

Now we can apply these estimates to age distributions of different locations.

```{r}

# USA
p_usa <- get_p_severe(country="United States of America")

# Bangladesh
p_bgd <- get_p_severe(country="Bangladesh")

# China
p_chn <- get_p_severe(country="China")

# Italy
p_ita <- get_p_severe(country="Italy")

# Switzerland
p_che <- get_p_severe(country="Switzerland")


p_data <- bind_rows(data.frame(Location = "USA", p_severe=p_usa$ests),
                    data.frame(Location = "China", p_severe=p_chn$ests),
                    data.frame(Location = "Bangladesh", p_severe=p_bgd$ests),
                    data.frame(Location = "Italy", p_severe=p_ita$ests),
                    data.frame(Location = "Switzerland", p_severe=p_che$ests)) %>%
  mutate(Location=factor(Location, levels=c("Bangladesh","China","USA","Switzerland","Italy"), ordered = TRUE))

# Make some boxplots
ggplot(p_data, aes(x=Location, y=p_severe)) +
  geom_boxplot(fill="maroon", color="darkred") + 
  ylab("Proportion Severe")
  
```




### Proportion Severe, Dagahaley expansion site
    
Now we need to apply the population structure of Dagahaley to estimate proportion hospitalized there.

```{r}

# pop_age <- read_csv(file.path("data",project,"age_dagahaley.csv"))
# age_smooth <- smooth.spline(pop_age$mid, pop_age$tot_per_year)
# pr_age <- predict(age_smooth, data.frame(mid=0:89)) %>% as.data.frame()
# pr_age <- pr_age %>% rename(age=mid, prop=mid.1) %>% mutate(prop = prop / sum(pr_age$mid.1))
# plot(pr_age$age, pr_age$prop)
# points(pop_age$mid, pop_age$tot_per_year, col="blue", pch=20)
# 
# # Get age by 10yr groups
# pr_age <- pr_age %>% mutate(age10 = floor(age/10)*10)
# pr_age10 <- pr_age %>% group_by(age10) %>% summarise(pr10 = sum(prop)) %>%
#     mutate(age = paste0(age10, "-", age10+9))
# pr_age10 <- as.numeric(pr_age10$pr10)
# pr_age10[8] <- sum(pr_age10[8:9])
# pr_age10 <- pr_age10[-9]
# names(pr_age10) <- 0:(length(pr_age10)-1)

### This is the code used to get the age distribution from the survey.
#  labs <- paste0(c(0,seq(10,70,10)), "-", c(seq(9,69, 10), 90))
#  agebins <- cut(dta$AgeInYear,
#                 breaks=c(seq(0,70,10),90),
#                 include.lowest = TRUE,
#                 right = FALSE,
#                 labels = labs)
# age_ <- table(agebins) / length(agebins)
# age_data <- data.frame(age_)
# colnames(age_data) <- c("age_group", "p")
# write_csv(age_data, "data/dagahaley/age_dagahaley.csv")


pr_age10 <- read_csv(file.path("data",project, "age_dagahaley.csv"))

# Estimate the proportion severe in the camp
p_severe_dagahaley <- get_p_severe_pop(pr_age10$p)
save(p_severe_dagahaley, file=file.path("results", project, "p_severe_dagahaley.RData"))



# PLOT IT
p_data <- bind_rows(p_data, data.frame(Location = stringr::str_to_title(project), p_severe=p_severe_dagahaley$ests)) %>%
  mutate(Location=factor(Location, 
                         levels=c(stringr::str_to_title(project), "Bangladesh","China","USA","Switzerland","Italy"), 
                         ordered = TRUE)) %>%
  mutate(col_ = ifelse(Location==stringr::str_to_title(project), 2, 1))

# Make some boxplots
fills <- c("1"="maroon", "2"="gold")
cols <- c("1"="darkred", "2"="goldenrod1")
plot_severity <- ggplot(p_data, aes(x=Location, y=p_severe, fill=factor(col_), colour=factor(col_))) +
                          geom_boxplot() + 
                          scale_color_manual(values=c("darkred", "goldenrod4")) +
                          scale_fill_manual(values=c("maroon", "goldenrod1")) +
                          ylab("Proportion Severe") +
                          theme(legend.position = "none")
                        

```

Based on this crude analysis, if we assume 75% of infections in those 70+ lead to hospitalization, and the odds of hospitalization given infection by age mirrors the odds of mortality by age, we find that the hospitalization rate in `r print(stringr::str_to_title(project))` is likely to be between 4.9-9.2%, compared with 14.0-21.8% in China. From these estimates, it is reasonable to assume infections in Dagahaley are 35-43% as likely to result in a hositalization, as compared to China.



# PARAMETERS

### R0 Estimates Check
```{r}
r0 <- c(2.68,2.24,0.3,1.44,2.1,3.2,7.05,2.4,2.4,4.7,6.6,
        3.24,2.45,1.48,3.1,1.6,3.11,2.5,2.6,2.2)

quantile(r0, c(0.025, .975))

```



## Model Parameters

```{r}

# Simulation specifics   ----------------------------------------------
n.sims <- 500 # simulations per R
n.Rs <- 20
run_time <- 550
start_date_="2020-03-15"
end_date <- "2022-01-01"
step.size <- 1/8
seeds <- 1
cores <- 4


# Transmission Characteristics ---------------------------------
# we are going to assume recovery has mean of 7 days from infection
# then we will use a beta consistent with our estimates from above
# https://github.com/midas-network/COVID-19/tree/master/parameter_estimates/2019_novel_coronavirus

# incubation period 5.2 days based on an estimate from Lauer et al. 2020
sigma <- 1/(5.2) # subtract 1 for latent period adjustment
# time from symptom onset to recovery  
n_Icomp <- 3 # number of I compartments (using 3 to capture Erlang distribution)
gamma <-  1/6 * n_Icomp 



# R0 Values  ----------------------------------------------

# Controlled transmission 
R0_low <- runif(n.Rs, 1.5,2)
# Moderate transmission
R0_mid <- runif(n.Rs, 2, 3)
# Inflated transmission (inflated by the diphtheria inflation factor)
R0_high <- runif(n.Rs, 2*1.65, 3*1.65)


# sample point estimates of our betas from above
betas_low <- R0_low   * gamma / n_Icomp
betas_mid <- R0_mid   * gamma / n_Icomp
betas_high <- R0_high * gamma / n_Icomp






# Hospitalization   ----------------------------------------------


# time from hospitalization to discharge mean= 11.5, sd=3.625
# time from hospitalization to death mean= 11.2, sd= 1.88
# Time to hospitalization among symptom-based, mean 4.65 days (95% CI 0.93-12.42) (Bi et al. 2020)
# Time from hospitalization to discharge,  11.5 days (95% CI 8.0-17.3) (Sanche et al. 2020)
# Time from hospitalization to death, 11.2 days (95% CI 8.7-14.9) (Sanche et al. 2020)

#p_hosp  <- c(p_severe_dagahaley, p_hosp_dagahaley_high)
p_death <- .1
p_ICU   <- 0.264
p_vent  <- 0.15

time_hosp_pars = c(1.23, 0.79)
time_death_pars = c(log(11.25), log(1.15))
time_disch_pars = c(log(11.5), log(1.22)) 

```



# MODEL
    
### Run the model 
We can do this locally or on a cluster if needed.

```{r, eval=FALSE}
betas <- betas_low
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="low",
                                   sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

betas <- betas_mid
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="mid", sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

betas <- betas_high
sim_res <- run_seir_model_parallel(project, n.sims=n.sims, N=N, betas=betas, R0_val="high", sigma=sigma,
                                   gamma=gamma,
                          seeds=seeds, start_date_=start_date_, step.size=step.size,
                          run_time=run_time, cores=cores)

```
    

   
### Low Beta
```{r, echo=FALSE, eval=FALSE}

R0_val <- "low"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val, "-",
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)


# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))


sim_res_full <- sim_hospdeath %>% dplyr::select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "Low") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_low <- sim_res_full
rm(sim_res)

# Save it
dir.create("results", recursive = TRUE, showWarnings = FALSE)
write_csv(sim_res_full, 
          file.path("results", project, paste0("sim_res_low_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```

    
    
    
### Mid Beta
      
```{r, echo=FALSE, eval=FALSE}

betas <- betas_mid

R0_val <- "mid"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val, "-",
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)



# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))



sim_res_full <- sim_hospdeath %>% select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "Mid") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_mid <- sim_res_full

# Save it
write_csv(sim_res_mid, 
          file.path("results", project, paste0("sim_res_mid", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```






### High Beta
```{r, echo=FALSE, eval=FALSE}

betas <- betas_high

R0_val <- "high"
sim_res <- read_csv(file.path("results", project, paste0("sim_res_nohosp_", R0_val,"-", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

sim_res <- sim_res %>%
    rename(time=date, incidI=incid) %>% 
    mutate(geoid = "KB_ES", sim_num=as.integer(sim_id)) %>%
    mutate(uid = paste0(geoid, "-", sim_num))


# Get Hospitalizations
sim_hospdeath <- build_hospdeath_par(
                            data=sim_res, p_hosp=p_severe_dagahaley, 
                            p_death, p_vent, p_ICU, p_hosp_type="gamma",
                            time_hosp_pars = c(1.23, 0.79), 
                            time_ICU_pars = c(log(10.5), log((10.5-7)/1.35)),
                            time_vent_pars = c(log(10.5), log((10.5-8)/1.35)),
                            time_death_pars = c(log(11.25), log(1.15)), 
                            time_disch_pars = c(log(11.5), log(1.22)),
                            time_ICUdur_pars = c(log(16), log(2.96)),
                            end_date = "2022-01-01",
                            length_geoid = 5,
                            cores=4, 
                            run_parallel=FALSE)
colnames(sim_hospdeath)


# Get simulation info to fill in where needed
sim_info <- sim_res %>% select(sim, beta_ind, sim_beta, sim_id, beta, seeds) %>% 
  filter(!duplicated(paste0(sim, beta_ind)))



sim_res_full <- sim_hospdeath %>% select(sim_beta, sim, beta_ind, sim_id, beta, seeds, time, day, everything()) %>%
  mutate(scenario = "High") %>% rename(t=time) %>%
  filter(!is.na(day))

sim_res_full <- sim_res_full %>% 
  arrange(sim_beta, t) %>%
  group_by(sim_beta) %>%
  mutate(cum_hosp = cumsum(incidH),
         cum_vent = cumsum(incidVent),
         cum_icu = cumsum(incidICU),
         cum_death = cumsum(incidD)) %>% ungroup()

sim_res_full <- sim_res_full %>% filter(!is.na(t))  


# Rename it
sim_res_high <- sim_res_full

# Save it
dir.create("results", recursive = TRUE, showWarnings = FALSE)
write_csv(sim_res_high,
          file.path("results", project, paste0("sim_res_high_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```




# RESULTS

### ~ Combine results

```{r, eval=FALSE}

sim_res <- full_join(full_join(sim_res_low %>% mutate(scenario="Low Transmission"),
                               sim_res_mid %>% mutate(scenario="Moderate Transmission")),
                               sim_res_high %>% mutate(scenario="High Transmission"))
sim_res$R <- sim_res$beta * n_Icomp / gamma
sim_res <- sim_res %>% mutate(scenario = factor(scenario, levels=c("Low Transmission", "Moderate Transmission", "High Transmission"), ordered = TRUE))

sim_res <- sim_res %>% filter(!is.na(sim))

write_csv(sim_res, 
          file.path("results", project, paste0("sim_res_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))

```


```{r, echo=FALSE}
sim_res <- read_csv(file.path("results", project, paste0("sim_res_", 
                      month.abb[lubridate::month(Sys.Date())],lubridate::day(Sys.Date()), ".csv")))
sim_res <- sim_res %>% 
  mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))
```





## TABLE 1  
        
```{r, echo=FALSE}

# Final Size - IN first 550 days
summ_ <- sim_res %>% as.data.frame() %>% group_by(sim_beta, scenario) %>% 
  summarise(final_size = max(cum_cases, na.rm=TRUE),
            max_daily_incid = max(incidI, na.rm=TRUE),
            max_daily_hosp  = max(incidH, na.rm=TRUE),
            max_daily_icu  = max(incidICU, na.rm=TRUE),
            max_daily_vent  = max(incidVent, na.rm=TRUE),
            max_daily_death  = max(incidD, na.rm=TRUE),
            max_curr_hosp   = max(hosp_curr, na.rm=TRUE),
            max_curr_icu   = max(icu_curr, na.rm=TRUE),
            #max_curr_vent   = max(vent_curr, na.rm=TRUE),
            final_death  = max(cum_death, na.rm=TRUE),
            final_hosp  = max(cum_hosp, na.rm=TRUE),
            final_vent  = max(cum_vent, na.rm=TRUE),
            final_icu  = max(cum_icu, na.rm=TRUE))

final_size_ <- summ_ %>% group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)),
            finalsize10 = mean(final_size>=10, na.rm=TRUE),
            finalsize100 = mean(final_size>=100, na.rm=TRUE),
            finalsize1000 = mean(final_size>=1000, na.rm=TRUE))

final_size_min100 <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)))

final_size_min1000 <- summ_ %>% filter(final_size>=1000) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_size, na.rm=TRUE),
            median = median(final_size, na.rm=TRUE),
            ll = quantile(final_size, prob=c(.0275)),
            ul = quantile(final_size, prob=c(.975)))

incid <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_daily_incid, na.rm=TRUE),
            median = median(max_daily_incid, na.rm=TRUE),
            ll = quantile(max_daily_incid, prob=c(.0275)),
            ul = quantile(max_daily_incid, prob=c(.975)))

hosps <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_hosp, na.rm=TRUE),
            median = median(final_hosp, na.rm=TRUE),
            ll = quantile(final_hosp, prob=c(.0275)),
            ul = quantile(final_hosp, prob=c(.975)))

curr_hosp <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_curr_hosp, na.rm=TRUE),
            median = median(max_curr_hosp, na.rm=TRUE),
            ll = quantile(max_curr_hosp, prob=c(.0275)),
            ul = quantile(max_curr_hosp, prob=c(.975)))

hosp_incid <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(max_daily_hosp, na.rm=TRUE),
            median = median(max_daily_hosp, na.rm=TRUE),
            ll = quantile(max_daily_hosp, prob=c(.0275)),
            ul = quantile(max_daily_hosp, prob=c(.975)))

deaths <- summ_ %>% filter(final_size>=100) %>%
  group_by(scenario) %>% 
  summarise(mean = mean(final_death, na.rm=TRUE),
            median = median(final_death, na.rm=TRUE),
            ll = quantile(final_death, prob=c(.0275)),
            ul = quantile(final_death, prob=c(.975)))

# Summarize day cum cases exceeds 100
hospexceeds <- sim_res %>% group_by(scenario, sim_beta) %>% 
  filter(cum_cases>250) %>%
  summarise( dayexceeds = min(day, na.rm=TRUE)) %>% group_by(scenario) %>%
  summarise(mean=mean(dayexceeds, na.rm=TRUE),
            ll = quantile(dayexceeds, .025, na.rm=TRUE), 
            ul = quantile(dayexceeds, .975, na.rm=TRUE))



table1 <- final_size_min100 %>% mutate(pr_outbreak=final_size_$finalsize100) %>%
  mutate(tot_inf = paste0(round(mean), " (",round(ll),"-",round(ul),")"),
          tot_hosp = paste0(round(hosps$mean), " (",round(hosps$ll),"-",round(hosps$ul),")"),
          tot_deaths = paste0(round(deaths$mean), " (",round(deaths$ll),"-",round(deaths$ul),")"),
          max_incid = paste0(round(incid$mean), " (",round(incid$ll),"-",round(incid$ul),")"),
          max_hosp_incid = paste0(round(hosp_incid$mean), " (",round(hosp_incid$ll),"-",round(hosp_incid$ul),")"),
          max_hosp_curr = paste0(round(curr_hosp$mean), " (",round(curr_hosp$ll),"-",round(curr_hosp$ul),")"),
          day_hosp_exceed = paste0(round(hospexceeds$mean), " (",round(hospexceeds$ll),"-",round(hospexceeds$ul),")"),) %>%
  select(scenario, pr_outbreak, tot_inf, tot_hosp, tot_deaths, max_incid, max_hosp_incid, max_hosp_curr, day_hosp_exceed)

table1
write_csv(table1, file.path("results", project, "Table1.csv"))


```






```{r, echo=FALSE}

# case_data <- read_csv("data/case_data.csv")
# hubei_cases <- case_data %>% filter(Province_State=="Hubei") %>% arrange(t)
# hubei_cases$est_infections <- hubei_cases$est_incid / p_hosp_china_low

sim_res_summ <- sim_res %>% group_by(scenario, day) %>% 
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

```




```{r, echo=FALSE}

sim_res_outbreaks <- sim_res %>% group_by(scenario, sim_beta) %>% 
  mutate(sim_max = max(cum_cases, na.rm = TRUE)) %>%
  filter(cum_cases > 100 ) 
  
sim_res_summ_outbreak <- sim_res_outbreaks %>% group_by(scenario, day) %>% 
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

```




## TABLE 2


```{r, echo=FALSE}

max_day_datahigh <- sim_res_outbreaks %>% filter(scenario=="High Transmission") %>% 
  group_by(sim_beta) %>% mutate(maxday = max(day), na.rm=TRUE) %>% ungroup() %>% filter(day==maxday)

max_day_datamid <- sim_res_outbreaks %>% filter(scenario=="Moderate Transmission") %>% 
  filter(day<=365) %>%
  group_by(sim_beta) %>% mutate(maxday = max(day), na.rm=TRUE) %>% ungroup() %>% filter(day==maxday)


sim_res_summ_outbreak_days <- sim_res_outbreaks %>% filter(day %in% c(30, 91, 182, 365)) %>%
  group_by(day, scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))

sim_res_summ_outbreak_daysHigh <- max_day_datahigh %>%
  group_by(scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))


sim_res_summ_outbreak_daysModerate <- max_day_datamid %>%
  group_by(scenario) %>%
  summarise(incid_mean = mean(incidI, na.rm=TRUE),
            cum_mean   = mean(cum_cases, na.rm=TRUE),
            hosp_incid_mean = mean(incidH, na.rm=TRUE),
            hosp_cum_mean = mean(cum_hosp, na.rm=TRUE),
            hosp_curr_mean = mean(hosp_curr, na.rm=TRUE),
            icu_cum_mean = mean(cum_icu, na.rm=TRUE),
            icu_curr_mean = mean(icu_curr, na.rm=TRUE),
            vent_cum_mean = mean(cum_vent, na.rm=TRUE),
            #vent_curr_mean = mean(vent_curr, na.rm=TRUE),
            death_incid_mean = mean(incidD, na.rm=TRUE),
            death_cum_mean = mean(cum_death, na.rm=TRUE),

            incid_ll = quantile(incidI, prob=.0275, na.rm=TRUE),
            cum_ll   = quantile(cum_cases, prob=.0275, na.rm=TRUE),
            hosp_incid_ll = quantile(incidH, prob=.0275, na.rm=TRUE),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275, na.rm=TRUE),
            hosp_curr_ll = quantile(hosp_curr, prob=.0275, na.rm=TRUE),
            icu_incid_ll = quantile(incidICU, prob=.0275, na.rm=TRUE),
            icu_cum_ll = quantile(cum_icu, prob=.0275, na.rm=TRUE),
            icu_curr_ll = quantile(icu_curr, prob=.0275, na.rm=TRUE),
            vent_incid_ll = quantile(incidVent, prob=.0275, na.rm=TRUE),
            vent_cum_ll = quantile(cum_vent, prob=.0275, na.rm=TRUE),
            #vent_curr_ll = quantile(vent_curr, prob=.0275, na.rm=TRUE),
            death_incid_ll = quantile(incidD, prob=.0275, na.rm=TRUE),
            death_cum_ll = quantile(cum_death, prob=.0275, na.rm=TRUE),
            
            incid_ul = quantile(incidI, prob=.975, na.rm=TRUE),
            cum_ul   = quantile(cum_cases, prob=.975, na.rm=TRUE),
            hosp_incid_ul = quantile(incidH, prob=.975, na.rm=TRUE),
            hosp_cum_ul = quantile(cum_hosp, prob=.975, na.rm=TRUE),
            hosp_curr_ul = quantile(hosp_curr, prob=.975, na.rm=TRUE),
            icu_cum_ul = quantile(cum_icu, prob=.975, na.rm=TRUE),
            icu_curr_ul = quantile(icu_curr, prob=.975, na.rm=TRUE),
            vent_cum_ul = quantile(cum_vent, prob=.975, na.rm=TRUE),
            #vent_curr_ul = quantile(vent_curr, prob=.975, na.rm=TRUE),
            death_incid_ul = quantile(incidD, prob=.975, na.rm=TRUE),
            death_cum_ul = quantile(cum_death, prob=.975, na.rm=TRUE))



sim_res_summ_outbreak_days <- bind_rows(sim_res_summ_outbreak_days,
                                        sim_res_summ_outbreak_daysModerate %>% mutate(day=365),
                                        sim_res_summ_outbreak_daysHigh %>% mutate(day=365))

table2 <- sim_res_summ_outbreak_days %>% group_by(scenario, day) %>%
  mutate(cum_inf = paste0(round(cum_mean), " (",round(cum_ll),"-",round(cum_ul),")"),
         cum_hosp = paste0(round(hosp_cum_mean), " (",round(hosp_cum_ll),"-",round(hosp_cum_ul),")"),
         cum_icu = paste0(round(icu_cum_mean), " (",round(icu_cum_ll),"-",round(icu_cum_ul),")"),
         cum_vent = paste0(round(vent_cum_mean), " (",round(vent_cum_ll),"-",round(vent_cum_ul),")"),
         cum_death = paste0(round(death_cum_mean), " (",round(death_cum_ll),"-",round(death_cum_ul),")")) %>%
  select(scenario, day, cum_inf, cum_hosp, cum_icu, cum_vent, cum_death)
  #mutate(scen_day = paste0(scenario," - ",day)) %>% select(-scenario, -day) 

table2
write_csv(table2, file.path("results", project, "Table2.csv"))


#View(data.frame(sim_res_summ_outbreak_days[,c(1:2)], round(sim_res_summ_outbreak_days[,-c(1:3)] / 600000,2)))


```


### Time intervals

```{r}

View(sim_res_summ_outbreak %>% filter(day==30) %>%
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))


View(sim_res_summ_outbreak %>% filter(day==60) %>% 
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))

View(sim_res_summ_outbreak %>% filter(day==90) %>% 
       summarise(
  inf = paste0(round(cum_mean), " (", round(cum_ll), "-", round(cum_ul),")"),
  hosp = paste0(round(hosp_cum_mean), " (", round(hosp_cum_ll), "-", round(hosp_cum_ul),")"),
  death = paste0(round(death_cum_mean), " (", round(death_cum_ll), "-", round(death_cum_ul),")")))


```






# FIGURES


### Age Distribution and Severity profiles
```{r, echo=FALSE}

plot_age <- ggplot(pr_age10, aes(x=age_group, y=p)) +
                    geom_bar(stat="identity", color="navyblue", fill="navyblue", width = .95) +
                    coord_flip() +
                    xlab("Proportion") +
                    ylab("Age (y)")

gridExtra::grid.arrange(plot_age, plot_severity, ncol=2)
ggsave(file.path("figures", project, "age_severity.png"), 
       gridExtra::grid.arrange(plot_age, plot_severity, ncol=2), 
       width=10, height=5, dpi=900, units = "in")

```

    
    

### 3-Curve Panel

```{r, echo=FALSE}

# Incid mean
sim_res_summ <- sim_res_summ %>% as.data.frame() %>%
                    mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))


pincid <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=incid_ll, ymax=incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    # geom_line(data=hubei_cases, aes(x=0:(nrow(hubei_cases)-1), y=est_infections), color="grey50", alpha=.5, size=1.5) +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.8),
          legend.title = element_blank()) +
          scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    ylab("Incident infections") + xlab("Day") +
  ggtitle("Estimated daily incident infections")

pincidhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    theme_classic() + 
    scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    #geom_hline(yintercept = 250, col="red", linetype="dashed") +
    theme(legend.position = "none") +
    ylab("Daily hospitalizations") + xlab("Day") +
  ggtitle("Estimated daily hospitalizations")

# pincidhosp_vHubei <- ggplot(data=sim_res_summ, aes(x=day)) +
#     geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
#     geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
#     geom_line(data=hubei_cases, aes(x=(0:(nrow(hubei_cases)-1)+30), y=est_incid), 
#               color="grey50", alpha=.5, size=1.5) +
#     #scale_y_continuous(trans="log") +
#     theme_classic() + 
#         scale_color_brewer(palette = "Set1", direction = -1) +
#     scale_fill_brewer(palette = "Set1", direction = -1) +
#       geom_hline(yintercept = 250, col="red", linetype="dashed") +
# 
#     theme(legend.position = "none") +
#     ylab("Daily hospitalizations") + xlab("Day") +
#   ggtitle("Estimated hospitalizations, Dagahaley refuge camp versus those observed in Hubei, China")

pinciddeath <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=death_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=death_incid_ll, ymax=death_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    theme_classic() + 
        scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
    theme(legend.position = "none") +
    ylab("Daily deaths") + xlab("Day") +
  ggtitle("Estimated daily deaths")



# Cum Infections
pcuminf <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=cum_ll, ymax=cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
        scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative infections") + xlab("Day") +
  ggtitle("Cumulative infections")


# Cum Hospitalizations
pcumhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_cum_ll, ymax=hosp_cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
      scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative hospitalizations") + xlab("Day") +
  ggtitle("Cumulative hospitalizations")


# Cum Deaths
pcumdeath <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=death_cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=death_cum_ll, ymax=death_cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    #theme(legend.position = c(0.8, 0.8)) +
      scale_color_brewer(palette = "Set2", direction = -1) +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    ylab("Cumulative deaths") + xlab("Day") +
  ggtitle("Cumulative deaths")


p_panel <- gridExtra::grid.arrange(pincid,pincidhosp,pinciddeath, nrow=3)
ggsave(file.path("figures", project, "sim_res_panel.png"), p_panel, width=8, height=10, dpi=900, units = "in")


```


### Hospitalization Capacity Needs

```{r, echo=FALSE}

# Current Hospitalizations
pcurrhosp <- ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_curr_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_curr_ll, ymax=hosp_curr_ul, group=scenario, fill=scenario), alpha=.3) + 
    geom_hline(yintercept = 250, col="red", linetype="dashed") +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
  theme(legend.position = c(0.8, 0.8),
          legend.title = element_blank()) +
    ylab("Current hospitalized") + xlab("Day") +
        scale_color_brewer(palette = "Set1", direction = -1) +
    scale_fill_brewer(palette = "Set1", direction = -1) +
  ggtitle("Daily hospitalization capacity required")


pcurrhosp
ggsave(file.path("figures", project, "curr_hosp.png"), width=8, height=4, dpi=600, units = "in")

```


### Day 20th Case

```{r, echo=FALSE}

sim_res_nooutbreak <- sim_res %>% group_by(scenario, sim_beta) %>% 
  mutate(max_cum = max(cum_cases)) %>% ungroup() %>%
  filter(max_cum <=1000) %>% 
  filter(cum_cases==max_cum) %>%
  group_by(scenario, sim_beta) %>% filter(day==max(day))

summary(sim_res_nooutbreak$max_cum)
hist(sim_res_nooutbreak$max_cum)



# First Date >20 cases
sim_res <- sim_res %>% as.data.frame() %>%
                    mutate(scenario = factor(scenario, 
                           levels=c("Low Transmission", "Moderate Transmission", 
                                    "High Transmission"), ordered = TRUE))

day20case <- sim_res %>% filter(cum_cases>=20) %>% group_by(sim_beta, scenario) %>% summarize(minday = min(day)) 
day20case_sum <- day20case %>% group_by(scenario) %>% 
  summarize(mean = mean(minday), 
            median = median(minday),
            ll = quantile(minday, prob=c(.0275)),
            ul = quantile(minday, prob=c(.975)))

p_day20 <- ggplot(day20case, aes(x=minday, group=scenario, fill=scenario)) + 
  geom_density(alpha=0.5) +
  theme_classic() + 
  coord_cartesian(xlim=c(0,150)) +
  xlab("Day") + 
  theme(legend.position = c(0.8, 0.8)) +
  ggtitle("Day on which cumulative cases reaches 20")
p_day20

ggsave(file.path("figures", project, "day_20th_case.png"), p_day20, width=8, height=4, dpi=900, units = "in")

```






```{r, echo=FALSE}
 
# ggplot() +
#     geom_line(data=sim_res, aes(x=date, y=incid, group=sim_id, color=beta)) + 
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()
# 
# ggplot() +
#     geom_line(data=sim_res, aes(x=date, y=cum_cases, group=sim_id, color=beta)) + 
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()
# 
# 
# ggplot() +
#     geom_line(data=sim_hospdeath, aes(x=t, y=hosp_curr, group=sim_beta, color=beta)) + 
#     scale_colour_gradient(low="yellow", high="red") +
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()
# 
# ggplot() +
#     geom_line(data=sim_hospdeath, aes(x=t, y=cum_hosp, group=sim_beta, color=beta)) + 
#     scale_colour_gradient(low="yellow", high="red") +
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()
# 
# ggplot() +
#     geom_line(data=sim_hospdeath, aes(x=t, y=cum_death, group=sim_beta, color=beta)) + 
#     scale_colour_gradient(low="yellow", high="red") +
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()



```




## DISCUSSION
       
          
    
### Hospitalization Rate Ratio   
```{r}
p_severe_dagahaley$mean / p_chn$mean

```
   

   
### Cumulative cases before hospitalizations

```{r, echo=FALSE}

hosp_1 <- sim_res %>% filter(cum_hosp>0) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))
# summary((hosp_1 %>% filter(scenario=="High Transmission"))$day)
# summary((hosp_1 %>% filter(scenario=="Moderate Transmission"))$day)
# summary((hosp_1 %>% filter(scenario=="Low Transmission"))$day)




hosp_10 <- sim_res %>% filter(cum_hosp>9) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))
# summary((hosp_10 %>% filter(scenario=="High Transmission"))$day)
# summary((hosp_10 %>% filter(scenario=="Moderate Transmission"))$day)
# summary((hosp_10 %>% filter(scenario=="Low Transmission"))$day)



hosp_20 <- sim_res %>% filter(cum_hosp>19) %>% group_by(scenario, sim_beta) %>% 
  filter(t == min(t)) %>% group_by(scenario) %>% 
  summarise(meanincid = mean(cum_exposed), ll = quantile(cum_exposed, c(.025)), ul = quantile(cum_exposed, c(.975)),
            day = mean(day), dayll = quantile(day, c(.025)), dayul = quantile(day, c(.975)))


print(hosp_1)
print(hosp_10)
print(hosp_20)

```



### Max hospitalization capacities

```{r, echo=FALSE}

hosp_capmax <- sim_res %>% filter(cum_cases>100) %>% group_by(scenario, sim_beta) %>% 
  mutate(max_hosp_cap = max(hosp_curr)) %>% ungroup() %>%
  filter(hosp_curr==max_hosp_cap) %>% group_by(scenario) %>% 
  summarise(maxhospday = mean(day), 
            ll = quantile(day, c(.025)), 
            ul = quantile(day, c(.975)))

print(hosp_capmax)

```


