---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE, message = F, warning = F, results = F}
require(knitr)
require(tidyverse)
require(gridExtra)
# require(rstan)
library(RColorBrewer)
library(RgoogleMaps)

options(scipen = 999)
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(echo=TRUE)

#knitr::opts_knit$set(root.dir = normalizePath("../"))

source("../R/DataLoadUtils.r")
source("../R/BasicEpiAnalyses.r")
source("../R/DataUtils.r")
# source("R/DataLoadUtils.r")
# source("R/BasicEpiAnalyses.r")
# source("R/DataUtils.r")

```






## AGE ADJUSTMENT
Age distribution data source: https://population.un.org/wpp/Download/Standard/Population/

```{r}

china_agepop <- get_age_pop("China")
bangladesh_agepop <- get_age_pop("Bangladesh")
#kutupalong_agepop <- get_age_pop("Bangladesh")



```




## ESTIMATE R0    

Now we can estimate the reproductive number ($R$), using a very simple method based on the rate of exponential growth of the epidemic. This requires that we know the generation time distribution for nCoV, which we don't know exactly. We account for this uncertainty in our calculations and come up with the following distribution of Rs consistent with our data: 

```{r,warning=FALSE,message=FALSE,echo=FALSE, eval=FALSE}
library(R0) # nice little package implementing a bunch of R estimation techniques
## 1) assuming a 8.4 day mean generation time, sd of 3.8 (approx. exponential for now). Borrowed from SARS in Singapore.
## source: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2760158/#R8
## 2) estimate below is based on dates of confirmed cases, but IDEALLY should be dates of onset or dates of hospital visits
## we are essentially assuming time for hospital visits to case confirmation is the same across all cases
## 3) MORE IMPORTANTLY, cases should be local transmission cases, not imported cases. MODIFY WHEN DATA IS AVAILABLE!!!!

Rest_loc_confirmed <- vector("list", length=n_loc)
mGT <- generation.time("gamma", c(mean=7.5,sd=3))
for (i in 1:n_loc){
    loc <- locations_full[i]
    incid_ <- as.numeric((incid_data_ %>% filter(Province_State == loc))$Incidence)
    #if (max(incid_)<7) next
    begin_ <- as.integer(min(which(incid_>0), na.rm=TRUE))
    end_ <- as.integer(max((begin_ + 7), which.max(incid_)[1]))
    Rest_loc_confirmed[[i]] <- est.R0.EG(incid_, GT=mGT, begin=begin_, end=end_)
}
point.estimates <- sapply(Rest_loc_confirmed,function(x) x$R)
names(point.estimates) <- locations_full

```

From this we get an estimated $R$ of r my.Rest.confirmed$R in the range of r my.Rest.confirmed$conf.int using the epi curve based on date of confirmed cases (IDEALLY SHOULD BE date of symptom onset, or date of hospital visit). This is a VERY simplistic (and imperfect) estimate and given the expansion of the epidemic to date, it probably isn't that high. Since we really don't know the generation time for nCoV, and we used the parameter estimated for SARS. We will now sample a bunch of different generation time distributions consistent with this to get a range of estimates for $R$.

```{r, warning=FALSE, message=FALSE, echo=FALSE, eval=FALSE}
set.seed(24514)

n.sims <- 50
mean.gen.times <- runif(n.sims,7,8) 
sd.gen.times <- runif(n.sims,1,6) # this is fairly arbitrary at the moment

R_locations <- data.frame(location = locations_full, R_mean=NA, R_lb=NA, R_ub=NA)

for (n in 1:n_loc){
     
    loc <- locations_full[n]
    incid_ <- as.numeric((incid_data_ %>% filter(Province_State == loc))$Incidence)
    #if (max(incid_)<7) next
    begin_ <- as.integer(min(which(incid_>0), na.rm=TRUE))
    end_ <- as.integer(max((begin_ + 7), which.max(incid_)[1]))

    Rests<- vector("list",length=n.sims)
    for (i in 1:n.sims){
      mGT <- generation.time("gamma", c(mean.gen.times[i], sd.gen.times[i]))
      # could impute some of the onset dates here later rather than a single imputation
      Rests[[i]] <- est.R0.EG(incid_, GT=mGT, begin=begin_, end=end_)
    }
    point.estimates <- sapply(Rests,function(x) x$R)
    
    R_locations[n, 2:4] <- round(c(mean(point.estimates), as.numeric(quantile(point.estimates,c(.025,.975)))),3)
}


Given these estimates of R what sort of progression may we expect in a 'homogeneous world' with a simple model starting from `r tail(incid_data_,1)[1]` moving forward a few weeks.

```



### Estimate Hospitalization Rate

#### ~ Prob Hosp - Reported Case-adjusted

```{r}

# Prob hosp by age in Mainland China (soure: https://github.com/cmrivers/ncov/blob/master/COVID-19.pdf)
ages_ <- c(0, 10, 20, 30, 40, 50, 60, 70, 80)
ncases_age <- c(416, 549, 3619, 7600, 8571, 10008, 8583, 3918, 1408)
cfr_age <- c(.002, .002, .002, .002, .004, .013, .036, .080, .148)
ncases_age / sum(ncases_age)

nage_china <- get_age_pop("China")
nage_china
nage_china / sum(nage_china)

nage_china[9] <- sum(nage_china[9:11])
nage_china <- nage_china[1:9]


# Fatality OR - from justins estimates
cfr_OR <- c(.10, .10, .10, .14, .16, 1, 5.88, 17.71) # will need updating
names(cfr_OR) <- c("0-9", "10-19", "20-29", "30-39", "40-49", "50-59", "60-69", "70-100")


p_hosp_age <- ncases_age / nage_china
odds_hosp_age <- (p_hosp_age / (1-p_hosp_age))
or_hosp_age <- odds_hosp_age / odds_hosp_age[6]


# if assume 75% of those aged 70-80 are hospitalized, we can get the proportions ...
#  x hosps age a = p_inf_hosp_age * p_infect * n_age
p_inf_hosp_age_70 <- .75


## Now we can get the probability of hospitalization by age
p_infect  <- ncases_age[8]  / ( p_inf_hosp_age_70 * nage_china[8] )
p_inf_hosp_age <- ncases_age / (p_infect * nage_china)
p_inf_hosp_age


## Now to check the overall hospitalization rate among infections estimate from this:
n_infections <- ncases_age / p_inf_hosp_age
n_infections
sum(n_infections)
sum(ncases_age)

# overall prop hospitalized
sum(ncases_age) / sum(n_infections)
# This seems very high



##-------------------------------------------------------------------
## Try again with only Hubei
pr_age <- c(.004, .004, .045, .131, .156, .22, .265, .126, .045, .005)
names(pr_age) <- seq(0,90,10)

nage_china <- get_age_pop("China")
ncases_age <- round(pr_age*33367)
nage_china_ <- nage_china
nage_china_[8] <- sum(nage_china_[8:11])
nage_china_ <- nage_china[-(9:11)]  

ncases_age[8] <- sum(ncases_age[8:10])
ncases_age <- ncases_age[-(9:10)]  

p_hosp_age <- ncases_age / nage_china_
odds_hosp_age <- (p_hosp_age / (1-p_hosp_age))
or_hosp_age <- odds_hosp_age / odds_hosp_age[6]


# if assume 75% of those aged 80+ are hospitalized, we can get the proportions ...
#  x hosps age a = p_inf_hosp_age * p_infect * n_age
p_inf_hosp_age_70 <- .75


## Now we can get the probability of hospitalization by age
p_infect  <- ncases_age[8]  / ( p_inf_hosp_age_70 * nage_china[8] )
p_inf_hosp_age <- ncases_age / (p_infect * nage_china_)
p_inf_hosp_age

## Now to check the overall hospitalization rate among infections estimate from this:
n_infections <- ncases_age / p_inf_hosp_age
n_infections
sum(n_infections)
sum(ncases_age)

# overall prop hospitalized
sum(ncases_age) / sum(n_infections)
# This seems a little high, but its a little more reasonable

# We will use this as the high capture scenario
p_inf_hosp_age_high <- p_inf_hosp_age
p_hosp_china_high <- sum(p_inf_hosp_age_high * (nage_china_ / sum(nage_china_)))
p_hosp_china_high
```


#### ~ Prob Hosp - CFR-adjusted
Let's do it again but using CFR for age adjustment

```{r}

# assume prob hosp for 70+ is .75
p_hosp_age70 <- .75 # if we wanted to get prob of death, this should be .15*.75
odds_hosp_age70 <- (p_hosp_age70 / (1-p_hosp_age70))
odds_hosp_age50 <- odds_hosp_age70 / cfr_OR[8]
odds_hosp <- cfr_OR * odds_hosp_age50 
p_inf_hosp_age <- odds_hosp / (1 + odds_hosp)

# combine last X age groups
nage_china <- get_age_pop("China")
ncases_age <- round(pr_age*33367)
ncases_age2 <- ncases_age
ncases_age2[8] <- sum(ncases_age2[8:10])
ncases_age2 <- ncases_age2[-(9:10)]

nage_china2 <- nage_china
nage_china2[8] <- sum(nage_china2[8:11])
nage_china2 <- nage_china2[-(9:11)]

## Now to check the overall hospitalization rate among infections estimate from this:
n_infections <- ncases_age2 / p_inf_hosp_age
n_infections
sum(n_infections)
sum(ncases_age2)

# overall prop hospitalized
sum(ncases_age2) / sum(n_infections)
# age-adjusted hospitization rate is ~6%

# double check with population structure
sum(p_inf_hosp_age * (nage_china2 / sum(nage_china2)))
# so about 14% of cases are being hospitalized in china, due to age structure

# We will use this as the low capture scenario
p_inf_hosp_age_low <- p_inf_hosp_age
p_hosp_china_low <- sum(p_inf_hosp_age_low * (nage_china2 / sum(nage_china2)))
p_hosp_china_low
```

This seems about right. we will use these estimates.


#### ~ Prop hospitalized - Kutupalong
Now we need to apply the population structure of Kutupalong to estimate proportion hospitalized there.

```{r}

pop_age <- read_csv("data/age_kutupalong.csv")
age_smooth <- smooth.spline(pop_age$mid, pop_age$tot_per_year)
pr_age <- predict(age_smooth, data.frame(mid=0:89)) %>% as.data.frame()
pr_age <- pr_age %>% rename(age=mid, prop=mid.1) %>% mutate(prop = prop / sum(pr_age$mid.1))
plot(pr_age$age, pr_age$prop)
points(pop_age$mid, pop_age$tot_per_year, col="blue", pch=20)

# Get age by 10yr groups
pr_age <- pr_age %>% mutate(age10 = floor(age/10)*10)
pr_age10 <- pr_age %>% group_by(age10) %>% summarise(pr10 = sum(prop)) %>%
    mutate(age = paste0(age10, "-", age10+9))
pr_age10_kutupalong <- as.numeric(pr_age10$pr10)
pr_age10_kutupalong[8] <- sum(pr_age10_kutupalong[8:9])
pr_age10_kutupalong <- pr_age10_kutupalong[-9]
names(pr_age10_kutupalong) <- 0:(length(pr_age10_kutupalong)-1)

# Apply to Kutupalong population structure - LOW capture
p_hosp_kutupalong_low <- sum(p_inf_hosp_age_low * pr_age10_kutupalong)
p_hosp_kutupalong_high <- sum(p_inf_hosp_age_high * pr_age10_kutupalong)
print(p_hosp_kutupalong_low)
print(p_hosp_kutupalong_high)

p_hosp_kutupalong_low / p_hosp_china_low
p_hosp_kutupalong_high / p_hosp_china_high



```

Based on this crude analysis, if we assume 75% of infections in those 70+ lead to hospitalization, and the odds of hospitalization given infection by age mirrors the odds of mortality by age, we find that the hospitalization rate in Kutupalong is likely to be between 4.9-9.2%, compared with 14.0-21.8% in China. From these estimates, it is reasonable to assume infections in Kutupalong are 35-43% as likely to result in a hositalization, as compared to China.


## Set Up Model

```{r}

# Simulation specifics
n.sims <- 50 # simulations per R
run_time <- 200


# bringing in simple model code for a stochastic model  
source("R/StochasticSEIR_wHosp.R") 

# Population Size - Kutupalong camp
N <- 8000000


# Transmission Characteristics ---------------------------------
# we are going to assume recovery has mean of 7 days from infection
# then we will use a beta consistent with our estimates from above
# https://github.com/midas-network/COVID-19/tree/master/parameter_estimates/2019_novel_coronavirus

# incubation period 5.2 days based on an estimate from Lauer et al. 2020
sigma <- 1/5.2 
# Time to hospitalization # Source: Hokkaido University
rho   <- 1/2.7 
# time from symptom onset to recovery  # Source: imperial college london
#gamma <-  1/((7.5-1/sigma)*2) 
#gamma <-  1/22.2
gamma <-  1/11.1  # use half of the recovery interval
# Time from hospitalization to discharge  # Source: Los Alamos Lab
# We are assuming no hospital transmission for simplicity
gamma2 <- 1/11.5

# Proportion hospitalized, adjusted for age distribution. This assumes the low capture scenario for China
# This assumes about half of cases reported in China may not actually require hospitalization
prop_hosp <- p_hosp_china_high


# R0 Values  ----------------------------------------------

# Controlled transmission (resembling Hubei right now)
R0_low <- runif(15, 1.25,1.6)

# Moderate transmission
R0_mid <- runif(15, 2.2,2.8)

# Inflated transmission
R0_high <- runif(15, 2.2*1.65, 2.8*1.65)


# sample point estimates of our betas from above
betas_low <- R0_low[sample(length(R0_low),n.sims,replace=T)] * gamma
betas_mid <- R0_mid[sample(length(R0_mid),n.sims,replace=T)] * gamma
betas_high <- R0_high[sample(length(R0_high),n.sims,replace=T)] * gamma


```




## MODEL - with Hospitalizations

```{r,echo=FALSE}

betas <- betas_low
sim_res <- NULL
for (b in seq_along(betas)){
  for (i in 1:n.sims){
    seeds <- 1#sample(10,1)
    tmp = runStochasticSEIR(beta = betas[b], sigma = sigma, gamma = gamma, gamma2 = gamma2, rho = rho,
                            prop_hosp = prop_hosp,
                            initial.state = c(S=N-seeds*2,E=seeds,I=seeds,H=0,R=0,I_trk=0, H_trk=0),
                            step.size = 1/8,
                            freq.dependent = TRUE, 
                            final.only = FALSE,
                            max.time = run_time,
                            import = NULL,
                            import.step.size = 1)
    
    # get epi curve by aggregtating 
    new.cases <- diff(tmp[,"I_trk"])
    new.hosps <- diff(tmp[,"H_trk"])

    days <- floor(tmp[,"time"])
    days_m1 <- days[-1]
    epi.curve <- tapply(new.cases,days_m1,sum) # sum up time steps by day
    hosp.incid.curve <- tapply(new.hosps,days_m1,sum) # sum up time steps by day
    hosp_daily_capac <- tapply(tmp[,"H"], days, max) # sum up time steps by day to get daily hospitalization capacities

    sim_res <- bind_rows(sim_res, data.frame(sim=i, beta_ind=b, beta=betas[b], day=unique(days), seeds=seeds,
                                             incid=epi.curve, incid_hosp = hosp.incid.curve, cum_cases=cumsum(epi.curve), 
                                             cum_hosp=cumsum(hosp.incid.curve), curr_hosp = hosp_daily_capac))
  }
}

start_date_ <- as.Date("2020-03-01")
dates <- seq.Date(as.Date(start_date_), as.Date(start_date_)+run_time-1, by=1)

sim_res$date <- start_date_ + sim_res$day
sim_res <- sim_res %>% arrange(sim, beta) %>% 
    mutate(sim_beta = paste0(sim, "-", beta_ind)) %>% 
    mutate(sim_id = as.integer(as.factor(sim_beta)))

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=incid, group=sim_id, color=beta)) + 
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=cum_cases, group=sim_id, color=beta)) + 
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=curr_hosp, group=sim_id, color=beta)) + 
    scale_colour_gradient(low="yellow", high="red") +
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=cum_hosp, group=sim_id, color=beta)) + 
    scale_colour_gradient(low="yellow", high="red") +
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()


# SUMMARIZE IT

sim_res_low <- sim_res


```



#### Estimate for Mid R0   

```{r}

betas <- betas_mid
sim_res <- NULL
for (b in seq_along(betas)){
  for (i in 1:n.sims){
    seeds <- 1#sample(10,1)
    tmp = runStochasticSEIR(beta = betas[b],
                            sigma = sigma,
                            gamma = gamma,
                            gamma2 = gamma2,
                            rho = rho,
                            prop_hosp = prop_hosp,
                            initial.state = c(S=N-seeds*2,E=seeds,I=seeds,H=0,R=0,I_trk=0, H_trk=0),
                            step.size = 1/8,
                            freq.dependent = TRUE,
                            final.only = FALSE,
                            max.time = run_time,
                            import = NULL,
                            import.step.size = 1)
    
    # get epi curve by aggregtating 
    new.cases <- diff(tmp[,"I_trk"])
    new.hosps <- diff(tmp[,"H_trk"])

    days <- floor(tmp[,"time"])
    days_m1 <- days[-1]
    epi.curve <- tapply(new.cases,days_m1,sum) # sum up time steps by day
    hosp.incid.curve <- tapply(new.hosps,days_m1,sum) # sum up time steps by day
    hosp_daily_capac <- tapply(tmp[,"H"], days, max) # sum up time steps by day to get daily hospitalization capacities

    sim_res <- bind_rows(sim_res, data.frame(sim=i, beta_ind=b, beta=betas[b], day=unique(days), seeds=seeds,
                                             incid=epi.curve, incid_hosp = hosp.incid.curve, cum_cases=cumsum(epi.curve), 
                                             cum_hosp=cumsum(hosp.incid.curve), curr_hosp = hosp_daily_capac))
}}

start_date_ <- as.Date("2020-03-01")
dates <- seq.Date(as.Date(start_date_), as.Date(start_date_)+run_time-1, by=1)

sim_res$date <- start_date_ + sim_res$day
sim_res <- sim_res %>% arrange(sim, beta) %>% 
    mutate(sim_beta = paste0(sim, "-", beta_ind)) %>% 
    mutate(sim_id = as.integer(as.factor(sim_beta)))

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=incid, group=sim_id, color=beta)) + 
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=curr_hosp, group=sim_id, color=beta)) + 
    scale_colour_gradient(low="yellow", high="red") +
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()


# Summarize it 
sim_res_mid <- sim_res


```




#### Estimate for High R0   

```{r}

betas <- betas_high
sim_res <- NULL
for (b in seq_along(betas)){
  for (i in 1:n.sims){
    seeds <- 1#sample(10,1)
    tmp = runStochasticSEIR(beta = betas[b],
                            sigma = sigma,
                            gamma = gamma,
                            gamma2 = gamma2,
                            rho = rho,
                            prop_hosp = prop_hosp,
                            initial.state = c(S=N-seeds*2,E=seeds,I=seeds,H=0,R=0,I_trk=0, H_trk=0),
                            step.size = 1/8,
                            freq.dependent = TRUE,
                            final.only = FALSE,
                            max.time = run_time,
                            import = NULL,
                            import.step.size = 1)
    
    # get epi curve by aggregtating 
    new.cases <- diff(tmp[,"I_trk"])
    new.hosps <- diff(tmp[,"H_trk"])

    days <- floor(tmp[,"time"])
    days_m1 <- days[-1]
    epi.curve <- tapply(new.cases,days_m1,sum) # sum up time steps by day
    hosp.incid.curve <- tapply(new.hosps,days_m1,sum) # sum up time steps by day
    hosp_daily_capac <- tapply(tmp[,"H"], days, max) # sum up time steps by day to get daily hospitalization capacities

    sim_res <- bind_rows(sim_res, data.frame(sim=i, beta_ind=b, beta=betas[b], day=unique(days), seeds=seeds,
                                             incid=epi.curve, incid_hosp = hosp.incid.curve, cum_cases=cumsum(epi.curve), 
                                             cum_hosp=cumsum(hosp.incid.curve), curr_hosp = hosp_daily_capac))
}}

start_date_ <- as.Date("2020-03-01")
dates <- seq.Date(as.Date(start_date_), as.Date(start_date_)+run_time-1, by=1)

sim_res$date <- start_date_ + sim_res$day
sim_res <- sim_res %>% arrange(sim, beta) %>% 
    mutate(sim_beta = paste0(sim, "-", beta_ind)) %>% 
    mutate(sim_id = as.integer(as.factor(sim_beta)))

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=incid, group=sim_id, color=beta)) + 
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

ggplot() +
    geom_line(data=sim_res, aes(x=date, y=curr_hosp, group=sim_id, color=beta)) + 
    scale_colour_gradient(low="yellow", high="red") +
    #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
    theme_classic()

sim_res_high <- sim_res


```

## SUMMARIZE RESULTS

### ~ Combine results

```{r}

sim_res <- full_join(full_join(sim_res_low %>% mutate(scenario="Low Transmission"),
                               sim_res_mid %>% mutate(scenario="Moderate Transmission")),
                     sim_res_high %>% mutate(scenario="High Transmission"))
sim_res$R <- sim_res$beta / gamma

sim_res <- sim_res %>% mutate(scenario = factor(scenario, levels=c("Low Transmission", "Moderate Transmission", "High Transmission"), ordered = TRUE))

write_csv(sim_res, "results/sim_res_Feb25.csv")
sim_res <- read_csv("results/sim_res_Feb25.csv")

```


### 

```{r}

# Final Size - IN first 360 days
summ_ <- sim_res %>% group_by(sim_beta, scenario) %>% summarise(final_size = max(cum_cases),
                                                        max_daily_incid = max(incid),
                                                        max_daily_hosp  = max(incid_hosp))
final_size_low <- data.frame(mean = mean(summ_$final_size), 
                             median = median(summ_$final_size),
                             ll = quantile(summ_$final_size, prob=c(.0275)),
                             ul = quantile(summ_$final_size, prob=c(.975)),
                             finalsize10 = mean(summ_$final_size<=10),
                             finalsize100 = mean(summ_$final_size<=100))
hist(summ_$final_size, breaks=100)



# First Date >10 cases
day10case <- sim_res %>% filter(cum_cases>=10) %>% group_by(sim_beta, scenario) %>% summarize(minday = min(day)) 
day10case_sum <- day10case %>% group_by(scenario) %>% 
  summarize(mean = mean(minday), 
            median = median(minday),
            ll = quantile(minday, prob=c(.0275)),
            ul = quantile(minday, prob=c(.975)))

p_day10 <- ggplot(day10case, aes(x=minday, group=scenario, fill=scenario)) + 
  geom_density(alpha=0.5) +
  theme_classic() + 
  coord_cartesian(xlim=c(0,50)) +
  xlab("Day") +
  ggtitle("Day on which cumulative cases reaches 10")
p_day10


# First Date >20 cases
day20case <- sim_res %>% filter(cum_cases>=20) %>% group_by(sim_beta, scenario) %>% summarize(minday = min(day)) 
day20case_sum <- day20case %>% group_by(scenario) %>% 
  summarize(mean = mean(minday), 
            median = median(minday),
            ll = quantile(minday, prob=c(.0275)),
            ul = quantile(minday, prob=c(.975)))

p_day20 <- ggplot(day20case, aes(x=minday, group=scenario, fill=scenario)) + 
  geom_density(alpha=0.5) +
  theme_classic() + 
  coord_cartesian(xlim=c(0,50)) +
  xlab("Day") + 
  theme(legend.position = c(0.8, 0.8)) +
  ggtitle("Day on which cumulative cases reaches 20")
p_day20

```



### ~ Plot Incidence Curve

```{r}
case_data <- read_csv("data/case_data.csv")
hubei_cases <- case_data %>% filter(Province_State=="Hubei") %>% arrange(t)
hubei_cases$est_infections <- hubei_cases$est_incid / .2

# ggplot() +
#     geom_line(data=sim_res, aes(x=date, y=incid, group=sim_id, color=beta)) + 
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()
# 
# ggplot() +
#     geom_line(data=sim_res, aes(x=date, y=curr_hosp, group=sim_id, color=beta)) + 
#     scale_colour_gradient(low="yellow", high="red") +
#     #coord_cartesian(xlim=c(as.Date("2020-01-15"), as.Date(Sys.Date())+14)) +
#     theme_classic()


sim_res_summ <- sim_res %>% group_by(scenario, day) %>% 
  summarise(incid_mean = mean(incid),
            cum_mean   = mean(cum_cases),
            hosp_incid_mean = mean(incid_hosp),
            hosp_cum_mean = mean(cum_hosp),
            hosp_curr_mean = mean(curr_hosp),
            
            incid_ll = quantile(incid, prob=.0275),
            cum_ll   = quantile(cum_cases, prob=.0275),
            hosp_incid_ll = quantile(incid_hosp, prob=.0275),
            hosp_cum_ll = quantile(cum_hosp, prob=.0275),
            hosp_curr_ll = quantile(curr_hosp, prob=.0275),
            
            incid_ul = quantile(incid, prob=.975),
            cum_ul   = quantile(cum_cases, prob=.975),
            hosp_incid_ul = quantile(incid_hosp, prob=.975),
            hosp_cum_ul = quantile(cum_hosp, prob=.975),
            hosp_curr_ul = quantile(curr_hosp, prob=.975))


ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=incid_ll, ymax=incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    geom_line(data=hubei_cases, aes(x=0:(nrow(hubei_cases)-1), y=est_infections), color="grey50", alpha=.3, size=2) +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.7)) +
    ylab("Daily cases") + xlab("Day") +
  ggtitle("Daily case counts for simulated outbreaks, Kutupalong Camp")


ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    geom_point(data=hubei_cases, aes(x=0:(nrow(hubei_cases)-1), y=est_incid), color="red", alpha=.25) +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.7)) +
    ylab("Daily hospitalizations") + xlab("Day") +
  ggtitle("Daily hospitizations for simulated outbreaks, Kutupalong Camp")



ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=cum_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=cum_ll, ymax=cum_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.7)) +
    ylab("Cumulative daily cases") + xlab("Day") +
  ggtitle("Cumulative case counts for simulated outbreaks, Kutupalong Camp")


ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_incid_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_incid_ll, ymax=hosp_incid_ul, group=scenario, fill=scenario), alpha=.3) + 
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.7)) +
    ylab("Daily cases") + xlab("Day") +
  ggtitle("Daily case counts for simulated outbreaks, Kutupalong Camp")


ggplot(data=sim_res_summ, aes(x=day)) +
    geom_line(aes(y=hosp_curr_mean, group=scenario, color=scenario)) + 
    geom_ribbon(aes(ymin=hosp_curr_ll, ymax=hosp_curr_ul, group=scenario, fill=scenario), alpha=.3) + 
    geom_hline(yintercept = 304, col="red", linetype="dashed") +
    #scale_y_continuous(trans="log") +
    theme_classic() + 
    theme(legend.position = c(0.8, 0.7)) +
    ylab("Current hospitalized") + xlab("Day") +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2") +
  ggtitle("Daily hospitalization counts for simulated outbreaks, Kutupalong Camp")




```





